Response to Reviewers - Article 4780

### 2024-01-11 review/B-response-V2.Rmd
respnse changed

We provide an overall summary of the changes made to the paper and the package and then we make a point-by-point explanation of how we addressed the reviewers' comments.

@@

  * It is nice to mention the challenges of all examples, as interested users of cubble could directly jump to the relevant example for their own use case. **\textcolor{purple}{No change made, current list at top of section 4 should be sufficient for readers to jump to the example that is most relevant for them.}**

>>>>

We appreciate the helpful and careful reviews. This is a point-by-point explanation of how we modified the paper to address the comments.

@@

  * It is nice to mention the challenges of all examples, as interested users of cubble could directly jump to the relevant example for their own use case. **\textcolor{purple}{No change made, paragraph at top of section 4 should be sufficient for readers to jump to the example that is most relevant for them.}**
